Understanding the drivers of diurnal and nocturnal urban land surface temperature

### 2018-04-23 report/article.tex
Updates from ShareLaTeX

@@

>>>>

\subsection{Variables related to Land Surface Temperature}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/holdout_results_r2.pdf}
\caption{ADD Caption}
\label{fig:cityholdout_errors}
\end{center}
\end{figure}

\subsection{Predicting Land Surface Temperature Between Cities}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/cities_holdout.pdf}
\caption{ADD Caption}
\label{fig:cityholdout_errors}
\end{center}
\end{figure}

@@

\section{Additional model results}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/holdout_results_mae.pdf}
\caption{ADD Caption}
\label{fig:cityholdout_errors}
\end{center}
\end{figure}
